Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-20 rapport.tex
doucement mais sûrement

@@

			\vspace{0.5em}
			\textbf{Phase 1: Preparation of the MPC-in-the-Head inputs.} For each iteration $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Derive randomness $r^{[e]}_{w}, r^{[e]}_r, r^{[e]}_{\psi}$ from the root seed $\rho$: \\
				\quad $(r^{[e]}_w, r^{[e]}_r, r^{[e]}_{\psi}) \leftarrow \text{PRG}(\texttt{salt}, e, \rho)$.

				\item Share the witness $w$ into an $(N-1)$-private linear secret sharing $[w^{[e]}_i]$: \\
				\quad $[X_1^{[e]}], [X_2^{[e]}], [Y_1^{[e]}], [Y_2^{[e]}], [R_A^{[e]}], [R_B^{[e]}] \leftarrow \text{Share}(w; r^{[e]}_w)$ \#The shares are in $\mathbb{F}_{q^k}$. \\
				\quad $[\vec{R}_y^{[e]}], [\vec{R}_y^{[e]}] \leftarrow \text{Share}(w; r^{[e]}_w)$ \#The shares are in $(\mathbb{F}_{q})^n$.

				\item Compute $X_1^{[e]}, X_2^{[e]}, Y_1^{[e]}, Y_2^{[e]}$ \\
				\quad $X_1^{[e]} \leftarrow \sum_{i=1}^{N} [X_1^{[e]}]^{\lir}$. \\
				\quad $X_2^{[e]} \leftarrow \sum_{i=1}^{N} [X_2^{[e]}]^{\lir}$. \\
				\quad $Y_1^{[e]} \leftarrow \sum_{i=1}^{N} [Y_1^{[e]}]^{\lir}$. \\
				\quad $Y_2^{[e]} \leftarrow \sum_{i=1}^{N} [Y_2^{[e]}]^{\lir}$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 2: First challenge (randomness for the MPC protocol).}
			\begin{enumerate}[label=\arabic*.]
				\item Expand $h_1$ as $(e^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_1)$.

				\item Compute random value $t_0^{[e]}$ and share it. \\
				\quad $[t_0^{[e]}]^{\lir} \leftarrow Hash_0(i || [\vec{R}_x^{[e]}]^{\lir}, [\vec{R}_y^{[e]}]^{\lir}, [X_1^{[e]}]^{\lir}, [X_2^{[e]}]^{\lir}, [Y_1^{[e]}]^{\lir}, [Y_2^{[e]}]^{\lir},$ \\ $[R_A^{[e]}]^{\lir}, [R_B^{[e]}]^{\lir} || \vec{\delta}_x^{[e]}, \vec{\delta}_y^{[e]}, \delta_A^{[e]}, \delta_B^{[e]})$. \\
				\quad $t_0^{[e]} \leftarrow \sum_{i=1}^{N} [t_0^{[e]}]^{\lir}$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 3: Simulation of the MPC protocol.} For each $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Compute $A^{[e]}$ and $B^{[e]}$ and share them: \\
				\quad $A^{[e]} \leftarrow X_1Y_1 - X_2Y_2$. \\
				\quad $B^{[e]} \leftarrow X_1(\vec{v} \cdot \vec{y}) + Y_1(\vec{u} \cdot \vec{x}) - X_2(\vec{u} \cdot \vec{y}) - Y_2(\vec{v} \cdot \vec{x})$. \\
				\quad $\delta_A^{[e]} \leftarrow A^{[e]} - \sum_{i=1}^{N} [R_A^{[e]}]^{\lir}$. \\
				\quad $\delta_B^{[e]} \leftarrow B^{[e]} - \sum_{i=1}^{N} [R_B^{[e]}]^{\lir}$. \\
				\quad $\vec{\delta}_x^{[e]} \leftarrow \vec{x}^{[e]} - \sum_{i=1}^{N} [\vec{R}_x^{[e]}]^{\lir}$. \\
				\quad $\vec{\delta}_y^{[e]} \leftarrow \vec{y}^{[e]} - \sum_{i=1}^{N} [\vec{R}_y^{[e]}]^{\lir}$.

								\item Compute the commitments \\
				\quad $View_i \leftarrow (
				[t_0^{[e]}]^{\lir},
				[(X_1 + t_0(\vec{u} \cdot \vec{x}))^{[e]}]^{\lir},
				[(X_2 + t_0(\vec{v} \cdot \vec{x}))^{[e]}]^{\lir},
				[(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{[e]}]^{\lir},
				[(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{[e]}]^{\lir},
				[(A + t_0 B)^{[e]}]^{\lir}
				)$. \\
				\quad $\texttt{com}^{[e]} := \text{Hash}_0(e, View_1, \dots, View_N, \vec{\delta}_x, \vec{\delta}_y, \delta_A, \delta_B)$

				\item Compute $h_1 := \text{Hash}(m, \texttt{salt}, \texttt{comm}^{[1]}, \dots, \texttt{comm}^{[\tau]})$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 4: Second challenge (parties to be opened).}
			\begin{enumerate}[label=\arabic*.]
				\item Compute $h_2 := \text{Hash}(\texttt{salt}, h_1, [\alpha^{[1]}]_{S}, \dots, [\alpha^{[\tau]}]_{S})$.
				\item Expand $h_2$ as $(I^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_2)$ where, for every $e, I^{[e]} \in [1:N]$ the party that will not be opened.
			\end{enumerate}

>>>>

	To lighten the notation, we will not write the index of the round, but all the sharing elements are per round $e \in [1, \tau]$.

@@

			\vspace{0.5em}
			\textbf{Phase 1: Preparation of the MPC-in-the-Head inputs.} For each iteration $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]				
				\item Share the witness $(\vec{x},\vec{y})$ into an $(N-1)$-private linear secret sharing $\vec{x}^{\lir}, \vec{y}^{\lir}$: \\
				\quad $\vec{R}_x^{\lir} = \text{PRG}(\texttt{"$R_x$ i"} \parallel salt \parallel e \parallel \rho)$ \\
				\quad $\vec{R}_y^{\lir} = \text{PRG}(\texttt{"$R_y$ i}\parallel salt \parallel e \parallel \rho)$ \\
				\quad $\vec{\delta}_x \leftarrow \vec{x} - \sum_{i=1}^{N} \vec{R}_x^{\lir}$. \\
				\quad $\vec{\delta}_y \leftarrow \vec{y} - \sum_{i=1}^{N} \vec{R}_y^{\lir}$.

				\item Prepare MPC protocol inputs\\
				\quad $X_1^{\lir} = \text{PRG}(\texttt{"$X_1$ i}\parallel salt \parallel e \parallel \rho)$ \\
				\quad $X_2^{\lir} = \text{PRG}(\texttt{"$X_2$ i}\parallel salt \parallel e \parallel \rho)$ \\
				\quad $Y_1^{\lir} = \text{PRG}(\texttt{"$Y_1$ i}\parallel salt \parallel e \parallel \rho)$ \\
				\quad $Y_2^{\lir} = \text{PRG}(\texttt{"$Y_2$ i}\parallel salt \parallel e \parallel \rho)$ \\
				\quad $R_A^{\lir} = \text{PRG}(\texttt{"$R_A$ i}\parallel salt \parallel e \parallel \rho)$ \\
				\quad $R_B^{\lir} = \text{PRG}(\texttt{"$R_B$ i}\parallel salt \parallel e \parallel \rho)$ \\

				\item Compute $X_1, X_2, Y_1, Y_2$ \\
				\quad $X_1 \leftarrow \sum_{i=1}^{N} X_1^{\lir}$. \\
				\quad $X_2 \leftarrow \sum_{i=1}^{N} X_2^{\lir}$. \\
				\quad $Y_1 \leftarrow \sum_{i=1}^{N} Y_1^{\lir}$. \\
				\quad $Y_2 \leftarrow \sum_{i=1}^{N} Y_2^{\lir}$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 2: First challenge (randomness for the MPC protocol).}
			\begin{enumerate}[label=\arabic*.]
				\item Compute random value $t_0^{\lir}$ for each round and each party. \\
				\quad $t_0^{\lir} \leftarrow Hash_0(
				i \parallel
				\vec{R}_x^{\lir},
				\vec{R}_y^{\lir},
				R_A^{\lir},
				R_B^{\lir},
				X_1^{\lir},
				X_2^{\lir},
				Y_1^{\lir},
				Y_2^{\lir} \parallel
				\vec{\delta}_x^{\lir},
				\vec{\delta}_y^{\lir},
				\delta_A^{\lir},
				\delta_B^{\lir}
				)$.

				\item Compute $t_0 \leftarrow \sum_{i=1}^{N} t_0^{\lir}$.
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 3: Simulation of the MPC protocol.} For each $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Compute $A$ and $B$ and share them: \\
				\quad $A \leftarrow X_1Y_1 - X_2Y_2$. \\
				\quad $B \leftarrow X_1(\vec{v} \cdot \vec{y}) + Y_1(\vec{u} \cdot \vec{x}) - X_2(\vec{u} \cdot \vec{y}) - Y_2(\vec{v} \cdot \vec{x})$. \\
				\quad $\delta_A \leftarrow A - \sum_{i=1}^{N} R_A^{\lir}$. \\
				\quad $\delta_B \leftarrow B - \sum_{i=1}^{N} R_B^{\lir}$. \\

				\item Compute the commitments \\
				\quad $View_i \leftarrow (
				t_0^{\lir},
				(X_1 + t_0(\vec{u} \cdot \vec{x}))^{\lir},
				(X_2 + t_0(\vec{v} \cdot \vec{x}))^{\lir},
				(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{\lir},
				(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{\lir},
				(A + t_0 B)^{\lir}
				)$. \\
				\quad $\texttt{com}^{[e]} := \text{Hash}_0(e, View_1, \dots, View_N, \vec{\delta}_x, \vec{\delta}_y, \delta_A, \delta_B)$
			\end{enumerate}

			\vspace{0.5em}
			\textbf{Phase 4: Second challenge (parties to be opened).}
			\begin{enumerate}[label=\arabic*.]
				\item Compute $h_2 := \text{Hash}(m, \texttt{salt}, \texttt{comm}^{[1]}, \dots, \texttt{comm}^{[\tau]})$.
				\item Expand $h_2$ as $(I^{[e]})_{e \in [1:\tau]} \leftarrow \text{Expand}(h_2)$ where, for every $e, I^{[e]} \in [1:N]$ the party that will not be opened.
			\end{enumerate}
